\begin{longtable}{>{\raggedright\arraybackslash}p{0.22\textwidth}>{\raggedright\arraybackslash}p{0.7\textwidth}}
\toprule
Alias & Blocking condition \\
\midrule
\endhead
gemini-2.0-flash & google:gemini-2.0-flash query failed: 429 RESOURCE\_EXHAUSTED. \{'error': \{'code': 429, 'message': 'You exceeded your current quota, please check your plan and billing details.... \\
gemini-2.5-pro & google:gemini-2.5-pro-preview-05-06 query failed after 5 retries: 404 NOT\_FOUND. \{'error': \{'code': 404, 'message': 'models/gemini-2.5-pro-preview-05-06 is not found for API... \\
gemma-2-27b & together:google/gemma-2-27b-it query failed: Error code: 401 - \{'id': 'oeScdEs-2kFHot-9e993ef559aa4615', 'error': \{'message': 'Invalid API key provided. You can find your API... \\
gemma-2-9b & together:google/gemma-2-9b-it query failed: Error code: 401 - \{'id': 'oeScdA5-2kFHot-9e993ef39f6ba694', 'error': \{'message': 'Invalid API key provided. You can find your API key... \\
gpt-4-turbo & openai:gpt-4-turbo query failed: Error code: 429 - \{'error': \{'message': 'You exceeded your current quota, please check your plan and billing details. For more information on... \\
gpt-4o & openai:gpt-4o query failed: Error code: 429 - \{'error': \{'message': 'You exceeded your current quota, please check your plan and billing details. For more information on this... \\
gpt-4o-mini & openai:gpt-4o-mini query failed: Error code: 429 - \{'error': \{'message': 'You exceeded your current quota, please check your plan and billing details. For more information on... \\
gpt-oss-120b & together:openai/gpt-oss-120b query failed: Error code: 401 - \{'id': 'oeScSe3-z1gNr-9e993e15ef806a00', 'error': \{'message': 'Invalid API key provided. You can find your API key... \\
llama-3.1-405b & together:meta-llama/Llama-3.1-405B-Instruct-Turbo query failed: Error code: 401 - \{'id': 'oeScd5Z-2kFHot-9e993ef22ea57bd8', 'error': \{'message': 'Invalid API key provided. You... \\
llama-3.1-70b & together:meta-llama/Llama-3.1-70B-Instruct-Turbo query failed: Error code: 401 - \{'id': 'oeScd1Y-2kFHot-9e993ef05bc9df6b', 'error': \{'message': 'Invalid API key provided. You... \\
llama-3.1-8b & together:meta-llama/Llama-3.1-8B-Instruct-Turbo query failed: Error code: 401 - \{'id': 'oeSccvd-2kFHot-9e993eeeaad4139d', 'error': \{'message': 'Invalid API key provided. You can... \\
mistral-nemo & together:mistralai/Mistral-Nemo-Instruct-2407 query failed: Error code: 401 - \{'id': 'oeScdZu-2kFHot-9e993efc1cdf2381', 'error': \{'message': 'Invalid API key provided. You can... \\
mixtral-8x22b & together:mistralai/Mixtral-8x22B-Instruct-v0.1 query failed: Error code: 401 - \{'id': 'oeScdQa-2kFHot-9e993ef88fb3bb96', 'error': \{'message': 'Invalid API key provided. You can... \\
\bottomrule
\end{longtable}
